Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2018-01-18 Thesis/Thesis.rnw
Minor cleanup

% TODO: Plot regression line in onset/offset analysis

@@

@@

Our goal was to construct a model of annual RSV incidence that allows us to easily estimate complex characteristics of RSV seasons, such as season onset and offset, or preventable RSV case fraction.

@@

% TODO: Dan says state next paragraph more clearly, it's important

@@

@@

Similarly, we assumed the protection by palivizumab is constant at 100\% throughout the protection period; however, not only is breakthrough RSV illness known to occur in patients on palivizumab, but it is an indication for discontinuing the remained of the prophylaxis regimen.

>>>>

% TODO: Plot regression line in onset/offset analysis
% TODO Erin: CL vs CI in abstract?
% TODO clarify all years analysis in figure captions
% TODO generally make figures stand more on their own
% TODO Put 1-2% punchline in the abstract, maybe
% TODO mention misalignment in results

@@

% TODO reword next paragraph

@@

Our goal was to construct a model of annual RSV incidence that allows us to easily estimate complex characteristics of RSV seasons, such as season onset and offset.

@@

% TODO: Dan says state next paragraph more clearly, it's important
% TODO: Hartford county is a lie

@@

% TODO data not shown

@@

Similarly, we assumed the protection by palivizumab is constant at 100\% throughout the protection period; however, not only is breakthrough RSV illness known to occur in patients on palivizumab, but it is an indication for discontinuing the remainder of the prophylaxis regimen.
